Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
change on final section and diagram position.

Once a variable is selected, we can find an estimate value of the energy corresponding to the chosen variable by measuring the average energy.
The method utilised predicts the ground state, the lowest possible energy level of an atom. The values of the variable and estimate energy are
then fed through a programme; this proposes settings for a new variable – let us call this variable $v_1$­. Comparing to our coffee example, it
 has been decided that either a new blend of coffee is necessary as the current coffee might be perhaps too strong!

This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation of the smallest eigenenergy. Figure \ref{VQE} illustrates the key outline of the VQE algorithm.
\begin{figure}[H]
\begin{center}
\includegraphics[scale=1]{VQEdiagram.pdf}
\end{center}
\caption{VQE flowchart}\label{VQE}
\end{figure}

@@

Shuhao Yang wrote the Introduction and History sections and the PEA section and box. James Mills wrote the Scientific Background and Conclusion
and Outlook sections and the Experimental Implementation section and box. Shanice St John wrote the Techniques in Paper section introduction and
the Main Achievement of Paper section, and the VQE section and box. However we all edited and redrafted together and interviewed the academics
whose opinions we quoted in the article. We would like to thank Dr Abolfazl Bayat, Prof. Dan Browne and Mikolaj Uryszek for kindly talking to
us and allowing us to quote them here.

>>>>

Once a variable is selected, we can find an estimate value of the energy corresponding to the chosen variable by measuring the average energy.
The method utilised predicts the ground state, the lowest possible energy level of an atom. The values of the variable and estimate energy are
then fed through a programme; this proposes settings for a new variable – let us call this variable $v_1$­. Comparing to our coffee example, it
 has been decided that either a new blend of coffee is necessary as the current coffee might be perhaps too strong!
\begin{figure}[H]
\begin{center}
\includegraphics[scale=1]{VQEdiagram.pdf}
\end{center}
\caption{VQE flowchart}\label{VQE}
\end{figure}
This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation of the smallest eigenenergy. Figure \ref{VQE} illustrates the key outline of the VQE algorithm.

@@

This article is inspired by Scalable quantum simulation of molecular energies \cite{o2016scalable}. Shuhao Yang wrote the Introduction and History sections and the PEA section and box. James Mills wrote the Scientific Background and Conclusion
and Outlook sections and the Experimental Implementation section and box. Shanice St John wrote the Techniques in Paper section introduction and
the Main Achievement of Paper section, and the VQE section and box. However we all edited and redrafted together and interviewed the academics
whose opinions we quoted in the article. We would like to thank Dr Abolfazl Bayat, Prof. Dan Browne and Mikolaj Uryszek for kindly talking to
us and allowing us to quote them here.
